Who introduced the bug? The importance of the previous commit

### 2016-01-28 paperMSR.tex
Updating

In spite of, some studies in bug seeding start with this implicit assumption, \textit{"This earlier change is the one that caused the later fixed"} \cite{williams2008szz} or \textit{"The lines affected in the process of fixing a bug are the same one that originated or seeded that bug"} \cite{izquierdo2011developers}. Even, we can find this assumption in tools that prevent for future bugs; \textit{"We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit"} \cite{fejzer2015supporting}. Opposite that, we think that there is not empirical evidence supporting this assumption and we conducted an observational study on fix-bugs, expend significantly effort locating the bug origins into the source code and understandig the possible cause taken into account the moment in which this line was inserted as well as the general context of the project.

The image \ref{fig:1} shows a clear example of we understand as responsible to cause the bug. In the image we can see three different versions of the same file in the history of the control version used in the project. The code on the left \textit{(1)} was written to fix the bug previously inserted, the code in the middle \textit{(2)} shows the moment in which the bug was inserted by \textit{31f08423} as the id of change,the previous commit. The code on the right \textit{(3)} is to ensure that in previous versions of the file did't exist the bug. In this example, the commit \textit{31f08423} inserted for first time the line in where the bug was. And, according to the description of the commit log that fix the bug \ref{fig:2}, this previous commit cause the failure on the system due to used a variable as string when had to be used as boolean keeping the concordance with the rest of the code.

>>>>

In spite of, some studies in bug seeding start with this implicit assumption, \textit{"This earlier change is the one that caused the later fixed"} \cite{williams2008szz} or \textit{"The lines affected in the process of fixing a bug are the same one that originated or seeded that bug"} \cite{izquierdo2011developers}. Also in \cite{pan2009toward}'s work describing the bug fix patterns we can find this assumption; \textit{"The version before the bug fix revision is the bug version"}. Even, we can find this assumption in tools that prevent for future bugs; \textit{"We assume that a change/commit is buggy if its modifications has been later altered by a bug-fix commit"} \cite{fejzer2015supporting}. Opposite that, we think that there is not empirical evidence supporting this assumption and we conducted an observational study on fix-bugs, expend significantly effort locating the bug origins into the source code and understandig the possible cause taken into account the moment in which this line was inserted as well as the general context of the project.

The image \ref{fig:1} shows a clear example of we understand as cause of the bug. In the image we can see three different versions of the same file in the history of the control version used in the project. The code on the left \textit{(1)} was written to fix the bug previously inserted, the code in the middle \textit{(2)} shows the moment in which the bug was inserted by \textit{31f08423} as the id of change,the previous commit. The code on the right \textit{(3)} is to ensure that in previous versions of the file did't exist the bug. In this example, the commit \textit{31f08423} inserted for first time the line in where the bug was. And, according to the description of the commit log that fix the bug \ref{fig:2}, this previous commit cause the failure on the system due to used a variable as string when had to be used as boolean keeping the concordance with the rest of the code.
